Results_setup

### 2020-06-09 src/Result_Setup.Rmd
reducing redundancies standardizing DFs

#this dataframe doesn't work

#don't run here, run in the MS file
#DF.HetC.MixedModel.HQ
#DF.HetC.MixedModel.HQ <- subset()

@@

MLH1.MM_interaction <- drop1(MLH1.MM.M1, test="Chisq")$`Pr(Chi)`[2]
MLH1.MM_sex <- anova(MLH1.MM.M1, MLH1.MM.M1.reduce.sex)$`Pr(>Chisq)`[2]
MLH1.MM_subp <- anova(MLH1.MM.M1, MLH1.MM.M1.reduce.subp)$`Pr(>Chisq)`[2]
MLH1.MM_strain<- MM.rand.pval <- exactRLRT(MLH1.MM.M1)$p.value

@@

```{r Female.specific.glm, echo=FALSE, eval=TRUE}

@@

MLH1.female.spc.glm.M2 <- glm(mean_co ~ strain, data= (female_mouse.avs_for.analysis %>% filter(subsp != "Cast") ) )
sum_MLH1.female.spc.glm.M2 <- summary(MLH1.female.spc.glm.M2)

#round(lm.female.strain_sum$coefficients[,c(1,4)],5)

#write.table(lm.female.strain_sum$coefficients, "~./MLH1repo/lm.female.strain.csv", sep=",",row.names = TRUE)
```

```{r Male.specific.glm, echo=FALSE, eval=TRUE}
#M4
MLH1.male.glm.M4 <- glm(mean_co ~ subsp * strain, data=(male_mouse.avs_for.analysis  %>% filter(subsp != "Cast") )   )

@@

# Q1 single bivalent section and total SC

@@

```{r Q1.total.SC_t.test, echo=FALSE}

#run t-test for male female avergage for each strain

#ALL
Q1_tot.sc_t.test.all <- t.test((mouse.total.skel %>% filter(sex == "male") %>% filter(species == "M.musculus") )$mean.skel,
                           (mouse.total.skel %>% filter(sex == "female") %>% filter(species == "M.musculus")  )$mean.skel)

#dom
Q1_tot.sc_t.test.DOM <- t.test((mouse.total.skel %>% filter(sex == "male") %>% filter(subsp == "Dom") )$mean.skel,
                           (mouse.total.skel %>% filter(sex == "female") %>% filter(subsp == "Dom") )$mean.skel)

#WSB
Q1_tot.sc_t.test.WSB <- t.test((mouse.total.skel %>% filter(sex == "male") %>% filter(strain == "WSB") )$mean.skel,
                           (mouse.total.skel %>% filter(sex == "female") %>% filter(strain == "WSB") )$mean.skel)
#G
Q1_tot.sc_t.test.G <- t.test((mouse.total.skel %>% filter(sex == "male") %>% filter(strain == "G") )$mean.skel,
                           (mouse.total.skel %>% filter(sex == "female") %>% filter(strain == "G") )$mean.skel)
#LEW
Q1_tot.sc_t.test.LEW <- t.test((mouse.total.skel %>% filter(sex == "male") %>% filter(strain == "LEW") )$mean.skel,
                           (mouse.total.skel %>% filter(sex == "female") %>% filter(strain == "LEW") )$mean.skel)

#Musc
Q1_tot.sc_t.test.MUSC <- t.test((mouse.total.skel %>% filter(sex == "male") %>% filter(subsp == "Musc") )$mean.skel,
                           (mouse.total.skel %>% filter(sex == "female") %>% filter(subsp == "Musc") )$mean.skel)

#PWD
Q1_tot.sc_t.test.PWD <- t.test((mouse.total.skel %>% filter(sex == "male") %>% filter(strain == "PWD") )$mean.skel,
                           (mouse.total.skel %>% filter(sex == "female") %>% filter(strain == "PWD") )$mean.skel)

#KAZ
Q1_tot.sc_t.test.KAZ <- t.test((mouse.total.skel %>% filter(sex == "male") %>% filter(strain == "KAZ") )$mean.skel,
                           (mouse.total.skel %>% filter(sex == "female") %>% filter(strain == "KAZ") )$mean.skel)

#SKIVE
#Q1_tot.sc_t.test.SKIVE <- t.test((totSC.mouse.av.table %>% filter(sex == "male") %>% filter(strain == "SKIVE") )$mean.skel,
#           (totSC.mouse.av.table %>% filter(sex == "female") %>% filter(strain == "SKIVE") )$mean.skel, paired = FALSE, alternative = #"greater")
#cell level total SC
#MLH1.merge.Skel   $skel_size
#error not enought female observations, ONLY 1 female SKIVE mouse

Q1_tot.scBIV_t.test.SKIVE <- t.test((Total.SC_DF %>% filter(sex == "male") %>% filter(strain == "SKIVE") )$skel_size,
           (Total.SC_DF %>% filter(sex == "female") %>% filter(strain == "SKIVE") )$skel_size   )

#MSM
Q1_tot.sc_t.test.MSM <- t.test((mouse.total.skel %>% filter(sex == "male") %>% filter(strain == "MSM") )$mean.skel,
                           (mouse.total.skel %>% filter(sex == "female") %>% filter(strain == "MSM") )$mean.skel)

```{r Q1.totSC_male.first.comp, echo=FALSE}

Q1.male.Dom.Musc.t.test <- t.test( ( mouse.total.skel %>% filter(sex == "male") %>% filter(subsp == "Dom") )$mean.skel,
(mouse.total.skel %>% filter(sex == "male") %>% filter(subsp == "Musc") )$mean.skel)

```{r Q1.M.lmer_totalSC, echo=FALSE, warning=FALSE, message=FALSE}

Q1.lmer_totSC.mouse.av.table <- mouse.total.skel %>% filter(strain != "AST" & strain != "TOM" & strain != "CZECH" & strain != "MOLF")

#str(Q1.lmer_totSC.mouse.av.table)

#unorder factors
Q1.lmer_totSC.mouse.av.table$subsp <- factor(Q1.lmer_totSC.mouse.av.table$subsp, ordered = FALSE)
Q1.lmer_totSC.mouse.av.table$sex <- factor(Q1.lmer_totSC.mouse.av.table$sex, ordered = FALSE)
Q1.lmer_totSC.mouse.av.table$strain <- factor(Q1.lmer_totSC.mouse.av.table$strain, ordered = FALSE)
Q1.lmer_totSC.mouse.av.table$species <- factor(Q1.lmer_totSC.mouse.av.table$species, ordered = FALSE)

#TOTAL SC AREA
lmer.Q1_mus.av_totSC <- lmer(mean.skel ~ subsp * sex + (1|strain), data=Q1.lmer_totSC.mouse.av.table, REML = TRUE)

lmer.Q1_mus.av_totSC_R.sex <- lmer(mean.skel ~ subsp + (1|strain), data=Q1.lmer_totSC.mouse.av.table, REML = TRUE)

lmer.Q1_mus.av_totSC_R.subsp <- lmer(mean.skel ~ sex + (1|strain), data=Q1.lmer_totSC.mouse.av.table, REML = TRUE)

lmer.Q1_mus.av_totSC_interaction  <-drop1(lmer.Q1_mus.av_totSC, test="Chisq" )$`Pr(Chi)`[2]

lmer.Q1_mus.av_totSC_sex  <-anova(lmer.Q1_mus.av_totSC, lmer.Q1_mus.av_totSC_R.sex)$`Pr(>Chisq)`[2]

lmer.Q1_mus.av_totSC_subp  <- anova(lmer.Q1_mus.av_totSC, lmer.Q1_mus.av_totSC_R.subsp)$`Pr(>Chisq)`[2]

lmer.Q1_mus.av_totSC_strain  <- exactRLRT(lmer.Q1_mus.av_totSC)$p.value

Q1.lmer.totSC_results <- data.frame(sub.sp = lmer.Q1_mus.av_totSC_subp, 
sex.results =  lmer.Q1_mus.av_totSC_sex, 
               interaction.pval = lmer.Q1_mus.av_totSC_interaction,  rand.pval = 
lmer.Q1_mus.av_totSC_strain)

@@

```{r Q1_SC.biv.short_ttest99, echo=FALSE, eval=FALSE}
#this show is re-dundant
#
#run t.tests for the mouse av. for reduced single bivalent datasets

#WSB
Q1_mus.av_shortSC_t.test.WSB <- t.test((Short.biv_mouse_table %>% filter(sex == "male") %>% filter(strain == "WSB") )$mean_SC,
                           (Short.biv_mouse_table %>% filter(sex == "female") %>% filter(strain == "WSB") )$mean_SC)

#G
Q1_mus.av_shortSC_t.test.G <- t.test((Short.biv_mouse_table %>% filter(sex == "male") %>% filter(strain == "G") )$mean_SC,
                           (Short.biv_mouse_table %>% filter(sex == "female") %>% filter(strain == "G") )$mean_SC)

#LEW
Q1_mus.av_shortSC_t.test.LEW <- t.test((Short.biv_mouse_table %>% filter(sex == "male") %>% filter(strain == "LEW") )$mean_SC,
                           (Short.biv_mouse_table %>% filter(sex == "female") %>% filter(strain == "LEW") )$mean_SC)

#PWD
Q1_mus.av_shortSC_t.test.PWD <- t.test((Short.biv_mouse_table %>% filter(sex == "male") %>% filter(strain == "PWD") )$mean_SC,
                           (Short.biv_mouse_table %>% filter(sex == "female") %>% filter(strain == "PWD") )$mean_SC)

#KAZ
Q1_mus.av_shortSC_t.test.KAZ <- t.test((Short.biv_mouse_table %>% filter(sex == "male") %>% filter(strain == "KAZ") )$mean_SC,
                           (Short.biv_mouse_table %>% filter(sex == "female") %>% filter(strain == "KAZ") )$mean_SC)

#SKIVE - this value used in the text
#only one SKVIE female, this is breaking the test
#Q1_mus.av_shortSC_t.test.SKIVE <- t.test(

#      (Short.biv_mouse_table %>% filter(sex == "male") %>% filter(strain == "SKIVE") )$mean_SC,
#      (Short.biv_mouse_table %>% filter(sex == "female") %>% filter(strain == "SKIVE") )$mean_SC
#      )

@@

```{r totSC_setup, echo=FALSE, eval = F}

#Total.SC_DF is the main dataframe and should be set up cleanly in the SetUpData.Rmd
#SC.skel.OG <- SC.skel #5683

tot.sc.x.list <- Total.SC_DF %>% filter(X == "X")

Total.SC_DF.og <- Total.SC_DF[! Total.SC_DF$Random.Name %in% tot.sc.x.list$Random.Name, ]
#quality is still a factor
str(Total.SC_DF.og)
Total.SC_DF.og$quality <- as.numeric(Total.SC_DF.og$quality)

Total.SC_DF.og <- Total.SC_DF.og %>% filter(quality < 5)

OG.MLH1.merge.Skel <- MLH1.merge.Skel #raw version of DF

#check for DUPs, #check for duplicatations of the random name
MLH1.merge.Skel$fileName  <- as.character(MLH1.merge.Skel$fileName)
tot.SC.dupies <- MLH1.merge.Skel[duplicated(MLH1.merge.Skel$ fileName ),]

MLH1.merge.Skel <- MLH1.merge.Skel %>% filter( X == "") %>% filter(REDO.crop == "no")

MLH1.merge.Skel$bin_size <- as.numeric(MLH1.merge.Skel$bin_size)
MLH1.merge.Skel$skel_size <- as.numeric(MLH1.merge.Skel$skel_size)
#table(MLH1.merge.Skel$category)

-- The total_SC outliers should be removed in the total.SC RData script

@@

where is total_SC M1?

@@

sum.Q1.glm_totSC_M2 <- summary(Q1.glm_totSC_M2)
sum.Q1.glm_totSC_M2$coefficients[,c(1,4)][8,]

@@

```{r Q1_short.M1, echo=FALSE}

@@

```{r Q1.glm_short.SC_M3, echo=FALSE, message=FALSE}

Q1.glm_short.SC_M3 <- glm(mean_SC ~ strain * sex, data= ( Short.biv_mouse_table %>% filter(species == "M.musculus") %>% filter(strain !=  "CAST" ) %>% filter(strain !=  "MOLF" ) %>% filter(strain !=  "HMI" ) %>% filter(strain !=  "AST" ) %>% filter(strain !=  "PERC" ) %>% filter(strain !=  "CZECH" ) )  )

#summary(Q1.glm_short.SC_M3)

summ.Q1.glm_short.SC_M3 <- summary(Q1.glm_short.SC_M3)

#round(summ.Q1.glm_short.SC_M3$coefficients[,c(1,4)],5)
#sex male very sig -- only sig
#sum.Q1.glm_totSC_M2$coefficients[,c(1,4)][8,]

#SKIVE * male
```

@@

Curated_BivData99 <- Curated_BivData[Curated_BivData$hand.foci.count < 5,]
Curated_BivData99 <- Curated_BivData99[(!is.na(Curated_BivData99$sex)),]

#adjust order of plot here
Curated_BivData99$strain <- factor(Curated_BivData99$strain,levels =c(
  "WSB","G","LEW","PERC",  
"PWD", "SKIVE",  "KAZ",
     "MSM", "MOLF",   
                     "CAST",
                         "SPRET","SPIC" ), order=T )

#nested boxplots, pooled Bivalents
Q1.SC.length_Nested_boxplots_Dom <- ggplot(Curated_BivData99[Curated_BivData99$subsp == "Dom",], aes(y = chromosomeLength, x=strain, fill=as.factor(hand.foci.count) ))+geom_boxplot(alpha=0.5)+ggtitle("Bivalent SC Lengths by Chrm Class \n Dom")+facet_wrap(subsp~sex, scales="free")+ylim(c(25,255))+theme(legend.position="none")

@@

```{r Q1.F1pos_long.short_setup, echo=FALSE, eval=FALSE}
#move to setup

Q1.long.biv_1CO <-  real.long.bivData %>% filter(species =="M.musculus") %>% filter(hand.foci.count == 1) %>% filter(strain != "MOLF") %>% filter(strain != "CZECH")

@@

@@

#make sure this dataset has all the right strains
Q1.Foci.pos_DF <- Mouse.Table_BivData_4MM %>% filter(strain != "CZECH") %>% filter(strain != "MOLF")

@@

@@

nrm.IFD_KAZ_BIV.data <- ggplot( (Curated_BivData %>% filter(strain =="KAZ" ) %>%  filter(hand.foci.count == "2") %>%  filter(sex == "male")  ) , aes(y = IFD1_PER, x= fileName, color=chromosomeLength))+geom_point()+ggtitle("Interfocal Distances, ABS KAZ")+facet_wrap(~mouse, scales = "free")+ylim(c(0,1))

nrm.IFD_KAZ.female_BIV.data <- ggplot( (Curated_BivData %>% filter(strain =="KAZ" ) %>%  filter(hand.foci.count == "2") %>%  filter(sex == "female")  ) , aes(y = IFD1_PER, x= fileName, color=chromosomeLength))+geom_point()+ggtitle("Normalized Interfocal Distances, female KAZ")+facet_wrap(~mouse, scales = "free")+ylim(c(0,1))
nrm.IFD_KAZ.female_BIV.data

@@

#M1_IFD_2CO_ABS
lmer.IFD.ABS_MM.M1 <- lmer(mean_IFD.2CO_ABS ~ subsp * sex + (1|strain), data=Mouse.Table_BivData_4MM, REML = TRUE) 
lmer.IFD.ABS_MM.M1.reduce.sex <- lmer( mean_IFD.2CO_ABS ~ subsp  +(1|strain), data=Mouse.Table_BivData_4MM )
lmer.IFD.ABS_MM.M1.reduce.subp <- lmer( mean_IFD.2CO_ABS ~ sex  +(1|strain), data=Mouse.Table_BivData_4MM )

#M1_IFD_2CO
lmer.IFD.PER_MM.M1 <- lmer(mean_IFD.2CO_PER ~ subsp * sex + (1|strain), data=Mouse.Table_BivData_4MM, REML = TRUE) 
lmer.IFD.PER_MM.M1.reduce.sex <- lmer( mean_IFD.2CO_PER ~ subsp  +(1|strain), data=Mouse.Table_BivData_4MM )
lmer.IFD.PER_MM.M1.reduce.subp <- lmer( mean_IFD.2CO_PER ~ sex  +(1|strain), data=Mouse.Table_BivData_4MM )

glm.Q1_IFD.ABS.M2  <- glm(mean_IFD.2CO_ABS ~ subsp * sex * strain, data=Mouse.Table_BivData_4MM  %>% filter(species == "M.musculus")  )
summry.glm.Q1_IFD.ABS.M2 <- summary(glm.Q1_IFD.ABS.M2)

glm.Q1_IFD.ABS.M2_kindaFU  <- glm(mean_IFD.2CO_ABS ~ subsp * sex * strain, data=mouse.level.BivData_table  %>% filter(species == "M.musculus")  )
summry.glm.Q1_IFD.ABS.M2_kindaFU <- summary(glm.Q1_IFD.ABS.M2_kindaFU)

#PER
glm.Q1_IFD.PER.M2 <- glm(mean_IFD.2CO_PER ~ subsp * sex * strain, data= (mouse.level.BivData_table %>% filter(species == "M.musculus") ) )
summry.glm.Q1_IFD.PER.M2 <- summary(glm.Q1_IFD.PER.M2)
```

glm.Q1_IFD.ABS.M3  <- glm(mean_IFD.2CO_ABS ~  sex * strain, data=Mouse.Table_BivData_4MM)
summry.glm.Q1_IFD.ABS.M3 <- summary(glm.Q1_IFD.ABS.M3)

#PER
glm.Q1_IFD.PER.M3  <- glm(mean_IFD.2CO_PER ~ sex * strain, data=Mouse.Table_BivData_4MM)
summry.glm.Q1_IFD.PER.M3 <- summary(glm.Q1_IFD.PER.M3)
#round(summry.glm.Q1_IFD.PER.M3$coefficients[,c(1,4)],5)

```{r Q1.IFD.long.short.setup, echo=FALSE, eval=FALSE}

Q1.IFD.long <- ddply(real.long.bivData, c("mouse"), summarise,

                      meanIFD2CO_raw = mean(IFD1_ABS[which(hand.foci.count == 2)], na.rm = TRUE),
                     meanIFD2CO_norm = mean(IFD1_PER[which(hand.foci.count == 2)], na.rm = TRUE)

Q1.IFD.long <- add_sex(Q1.IFD.long)
Q1.IFD.long <- add_strain(Q1.IFD.long)
Q1.IFD.long <- add_subsp(Q1.IFD.long)

Q1.IFD.long$strain <- factor(Q1.IFD.long$strain, ordered = FALSE)
Q1.IFD.long$subsp <- factor(Q1.IFD.long$subsp, ordered = FALSE)

Q1.IFD.short <- ddply(real.short.bivData, c("mouse"), summarise,

                      meanIFD2CO_raw = mean(IFD1_ABS[which(hand.foci.count == 2)], na.rm = TRUE),
                     meanIFD2CO_norm = mean(IFD1_PER[which(hand.foci.count == 2)], na.rm = TRUE)

Q1.IFD.short <- add_sex(Q1.IFD.short)
Q1.IFD.short <- add_strain(Q1.IFD.short)
Q1.IFD.short <- add_subsp(Q1.IFD.short)

Q1.IFD.short$strain <- factor(Q1.IFD.short$strain, ordered = FALSE)
Q1.IFD.short$subsp <- factor(Q1.IFD.short$subsp, ordered = FALSE)

#t.test. mouse av
Q1.IFD.raw_short.ttest_KAZ <-  t.test( (Q1.IFD.short %>% filter(sex == "male") %>% filter(strain =="KAZ" ))$meanIFD2CO_norm,
                                ( Q1.IFD.short %>% filter(sex == "female") %>% filter(strain =="KAZ"))$meanIFD2CO_norm)

Q1.IFD.raw_long.ttest_KAZ <- t.test( (Q1.IFD.long %>% filter(sex == "male") %>% filter(strain =="KAZ" ))$meanIFD2CO_norm,
                                ( Q1.IFD.long %>% filter(sex == "female") %>% filter(strain =="KAZ"))$meanIFD2CO_norm)
#both the short and long norm IFD are NS

#t.test Biv
Q1.IFD.raw_BIV.long.ttest_KAZ <-  t.test( (real.long.bivData %>% filter(sex == "male") %>% filter(strain =="KAZ" )  %>% filter(hand.foci.count == "2") )$IFD1_PER,
                ( real.long.bivData %>% filter(sex == "female") %>% filter(strain =="KAZ") %>%  filter(hand.foci.count == "2"))$IFD1_PER)

Q1.IFD.raw_BIV.short.ttest_KAZ <-  t.test( (real.short.bivData %>% filter(sex == "male") %>% filter(strain =="KAZ" )  %>% filter(hand.foci.count == "2") )$IFD1_PER,
                ( real.short.bivData %>% filter(sex == "female") %>% filter(strain =="KAZ") %>%  filter(hand.foci.count == "2"))$IFD1_PER)
```

@@

@@

```{r Q2totalSC_checkdates, echo=FALSE, eval=FALSE}

#investigating potential skew / technical effects in the algorithm

Neg.control <- ggplot(bep, aes(x=mean.skel, y=mean.bin, color=strain))+geom_point()+
  scale_color_manual(values=colors_of_strains)+ggtitle("Total SC by mean CO\nMouse Means")
#not sure what my expectations for this plot are,

median(bep$oldest.image.date) #"2017-08-03"
#there might be an issue with the algorithm performance 
#given the parrelle diagonal lines -- 
#this might be due to the dates imaged  2017-02-07

bep$date.cut.off <- ifelse( bep$oldest.image.date < "2017-02-07", 0, 1 )

Neg.control.find.date <- ggplot(bep, aes(x=mean.skel, y=mean.bin, color=strain))+geom_point()+
  scale_color_manual(values=colors_of_strains)+ggtitle("Total SC by mean CO\nMouse Means")+facet_wrap(~date.cut.off)

#there's evidence that the algorithm might have some biased effects -- 
#that will be investigated later.

@@

The molf male t-tests don't work because I only have total Sc measures for 1 MOLF male. to of the

```{r Q2.totSC.ttest_old, echo=FALSE, eval=FALSE}

#move this to MS_v2?

Q2tot.sc_t.test_High.Low <- t.test((mouse.total.skel %>% filter(sex == "male") %>% filter(Rec.group == "0") )$mean.skel,
                (mouse.total.skel %>% filter(sex == "male") %>% filter(Rec.group == "1") )$mean.skel)
#p-value = 0.007

#mol -- not enough Mol observations
#Q2tot.sc_t.test_High.Low_Mol <- t.test((mouse.total.skel %>% filter(sex == "male") %>% filter(Rec.group == "0") %>% filter(subsp == "Mol") )$mean.skel,
#         (mouse.total.skel %>% filter(sex == "male") %>% filter(Rec.group == "1") %>% filter(subsp == "Mol") )$mean.skel)

todo list if I get back to lab.

@@

@@

#DOM-MUSC-ALL
Q2.all.BIV_t.test_DomMusc <- t.test((Curated_BivData %>%filter(subsp == "Dom")%>%filter(sex == "male") )$chromosomeLength,
              (Curated_BivData %>% filter(subsp == "Musc")%>%filter(sex == "male"))$chromosomeLength)
#p-value = 4e-13

#DOM-MOL-ALL
Q2.all.BIV_t.test_DomMol <- t.test((Curated_BivData%>%filter(subsp == "Dom")%>%filter(sex == "male") )$chromosomeLength,
              (Curated_BivData %>% filter(subsp == "Mol")%>%filter(sex == "male"))$chromosomeLength)
#p-value = 6e-10

@@

Q2.SC_BivData_low.rec <- Curated_BivData %>% filter(sex=="male") %>% filter( hand.foci.count < 5)%>% filter(Rec.group == 0 )
Q2.SC_BivData_high.rec <- Curated_BivData %>% filter(sex=="male") %>% filter( hand.foci.count < 5) %>% filter(Rec.group == 1 )

@@

Curated_BivData99 <- Curated_BivData[Curated_BivData$hand.foci.count < 5,]
Curated_BivData99 <- Curated_BivData99[(!is.na(Curated_BivData99$sex)),]

#adjust order of plot here
Curated_BivData99$strain <- factor(Curated_BivData99$strain,levels =c(
  "WSB","G","LEW","PERC",  
"PWD", "SKIVE",  "KAZ",
     "MSM", "MOLF",   
                     "CAST",
                         "SPRET","SPIC" ), order=T )

Q2.SC_BivData <- Curated_BivData %>% filter(sex=="male") %>% filter( hand.foci.count < 5)

@@

mouse.level.BivData_table <- add_species(mouse.level.BivData_table)

>>>>

@@

MLH1.MM_interaction <- drop1(MLH1.MM.M1, test="Chisq")$`Pr(Chi)`[2]
MLH1.MM_sex <- anova(MLH1.MM.M1, MLH1.MM.M1.reduce.sex)$`Pr(>Chisq)`[2]
MLH1.MM_subp <- anova(MLH1.MM.M1, MLH1.MM.M1.reduce.subp)$`Pr(>Chisq)`[2]
MLH1.MM_strain <- exactRLRT(MLH1.MM.M1)$p.value

@@

```{r Female.specific.glm.M4.M5, echo=FALSE, eval=TRUE}

@@

MLH1.female.spc.glm.M5 <- glm(mean_co ~ strain, data= (female_mouse.avs_for.analysis %>% filter(subsp != "Cast") ) )
sum_MLH1.female.spc.glm.M5 <- summary(MLH1.female.spc.glm.M5)

#round(lm.female.strain_sum$coefficients[,c(1,4)],5)
#write.table(lm.female.strain_sum$coefficients, "~./MLH1repo/lm.female.strain.csv", sep=",",row.names = TRUE)
```

```{r Male.specific.glm.M4.M5, echo=FALSE, eval=TRUE}
#M4
MLH1.male.glm.M4 <- glm(mean_co ~ subsp * strain, data=(male_mouse.avs_for.analysis  %>% filter(subsp != "Cast") )   )

@@

# Q1 single bivalent

@@

@@

@@

@@

@@

sum.Q1.glm_totSC_M2 <- summary(Q1.glm_totSC_M2)
#sum.Q1.glm_totSC_M2$coefficients[,c(1,4)][8,]

@@

```{r Q1_SC_short.M1, echo=FALSE}

@@

```{r Q1.glm_short.SC_M3, echo=FALSE, message=FALSE}
Q1.glm_short.SC_M3 <- glm(mean_SC ~ strain * sex, data= ( Short.biv_mouse_table %>% filter(species == "M.musculus") %>% filter(strain !=  "CAST" ) %>% filter(strain !=  "MOLF" ) %>% filter(strain !=  "HMI" ) %>% filter(strain !=  "AST" ) %>% filter(strain !=  "PERC" ) %>% filter(strain !=  "CZECH" ) )  )

#summary(Q1.glm_short.SC_M3)
summ.Q1.glm_short.SC_M3 <- summary(Q1.glm_short.SC_M3)

#round(summ.Q1.glm_short.SC_M3$coefficients[,c(1,4)],5)
#sex male very sig -- only sig
#sum.Q1.glm_totSC_M2$coefficients[,c(1,4)][8,]
#SKIVE * male
```

@@

#nested boxplots, pooled Bivalents
Q1.SC.length_Nested_boxplots_Dom <- ggplot(cleanCurated_BivData[cleanCurated_BivData$subsp == "Dom",], aes(y = chromosomeLength, x=strain, fill=as.factor(hand.foci.count) ))+geom_boxplot(alpha=0.5)+ggtitle("Bivalent SC Lengths by Chrm Class \n Dom")+facet_wrap(subsp~sex, scales="free")+ylim(c(25,255))+theme(legend.position="none")

@@

@@

#SKIVE
Q1_1CO.pos_t.test.SKIVE <- t.test((mouse.level.BivData_table %>% filter(sex == "male") %>% filter(strain == "SKIVE") )$norm.first.foci.pos,
                           (mouse.level.BivData_table %>% filter(sex == "female") %>% filter(strain == "SKIVE") )$norm.first.foci.pos)

@@

@@

#M1_IFD_2CO_ABS
lmer.IFD.ABS_MM.M1 <- lmer(mean_IFD.2CO_ABS ~ subsp * sex + (1|strain), data= ( mouse.level.BivData_table %>% filter(strain != "CZECH") )) 
lmer.IFD.ABS_MM.M1.reduce.sex <- lmer( mean_IFD.2CO_ABS ~ subsp  +(1|strain), data=( mouse.level.BivData_table %>% filter(strain != "CZECH") ) )
lmer.IFD.ABS_MM.M1.reduce.subp <- lmer( mean_IFD.2CO_ABS ~ sex  +(1|strain), data=( mouse.level.BivData_table %>% filter(strain != "CZECH") ) )

#M1_IFD_2CO
lmer.IFD.PER_MM.M1 <- lmer(mean_IFD.2CO_PER ~ subsp * sex + (1|strain), data=( mouse.level.BivData_table %>% filter(strain != "CZECH") ) ) 
lmer.IFD.PER_MM.M1.reduce.sex <- lmer( mean_IFD.2CO_PER ~ subsp  +(1|strain), data=( mouse.level.BivData_table %>% filter(strain != "CZECH") )  )
lmer.IFD.PER_MM.M1.reduce.subp <- lmer( mean_IFD.2CO_PER ~ sex  +(1|strain), data=( mouse.level.BivData_table %>% filter(strain != "CZECH") ) )

glm.Q1_IFD.ABS.M2  <- glm(mean_IFD.2CO_ABS ~ subsp * sex * strain, data= ( mouse.level.BivData_table %>% filter(strain != "CZECH") )  )
summry.glm.Q1_IFD.ABS.M2 <- summary(glm.Q1_IFD.ABS.M2)

#PER
glm.Q1_IFD.PER.M2 <- glm(mean_IFD.2CO_PER ~ subsp * sex * strain, data= ( mouse.level.BivData_table %>% filter(strain != "CZECH") ) )
summry.glm.Q1_IFD.PER.M2 <- summary(glm.Q1_IFD.PER.M2)

glm.Q1_IFD.ABS.M3  <- glm(mean_IFD.2CO_ABS ~  sex * strain, data=( mouse.level.BivData_table %>% filter(strain != "CZECH") ))
summry.glm.Q1_IFD.ABS.M3 <- summary(glm.Q1_IFD.ABS.M3)

#PER
glm.Q1_IFD.PER.M3  <- glm(mean_IFD.2CO_PER ~ sex * strain, data=( mouse.level.BivData_table %>% filter(strain != "CZECH") ) )
summry.glm.Q1_IFD.PER.M3 <- summary(glm.Q1_IFD.PER.M3)
#round(summry.glm.Q1_IFD.PER.M3$coefficients[,c(1,4)],5)

```{r Q1.IFD_glm.M4.M5_female, echo=FALSE}

glm.Q1_IFD.ABS.M4.female  <- glm(mean_IFD.2CO_PER ~ subsp * strain, data= (mouse.level.BivData_table %>% filter(sex == "female") ) )
summry.glm.Q1_IFD.ABS.M4.female  <- summary(glm.Q1_IFD.ABS.M4.female)

glm.Q1_IFD.PER.M4.female  <- glm(mean_IFD.2CO_PER ~ subsp * strain, data= (mouse.level.BivData_table %>% filter(sex == "female") ) )
summry.glm.Q1_IFD.PER.M4.female  <- summary(glm.Q1_IFD.PER.M4.female)

#M5
glm.Q1_IFD.ABS.M5.female  <- glm(mean_IFD.2CO_PER ~  strain, data= (mouse.level.BivData_table %>% filter(sex == "female") ) )
summry.glm.Q1_IFD.ABS.M5.female  <- summary(glm.Q1_IFD.ABS.M4.female)

glm.Q1_IFD.PER.M5.female  <- glm(mean_IFD.2CO_PER ~  strain, data= (mouse.level.BivData_table %>% filter(sex == "female") ) )
summry.glm.Q1_IFD.PER.M5.female  <- summary(glm.Q1_IFD.PER.M5.female)

```{r Q1.IFD_glm.M4.M5_male, echo=FALSE}

glm.Q1_IFD.ABS.M4.male  <- glm(mean_IFD.2CO_PER ~ subsp * strain, data= (mouse.level.BivData_table %>% filter(sex == "male") ) )
summry.glm.Q1_IFD.ABS.M4.male  <- summary(glm.Q1_IFD.ABS.M4.male)

glm.Q1_IFD.PER.M4.male  <- glm(mean_IFD.2CO_PER ~ subsp * strain, data= (mouse.level.BivData_table %>% filter(sex == "male") ) )
summry.glm.Q1_IFD.PER.M4.male  <- summary(glm.Q1_IFD.PER.M4.male)

#M5
glm.Q1_IFD.ABS.M5.male  <- glm(mean_IFD.2CO_PER ~  strain, data= (mouse.level.BivData_table %>% filter(sex == "male") ) )
summry.glm.Q1_IFD.ABS.M5.male  <- summary(glm.Q1_IFD.ABS.M4.male)

glm.Q1_IFD.PER.M5.male  <- glm(mean_IFD.2CO_PER ~  strain, data= (mouse.level.BivData_table %>% filter(sex == "male") ) )
summry.glm.Q1_IFD.PER.M5.male  <- summary(glm.Q1_IFD.PER.M5.male)

@@

nrm.IFD_KAZ_BIV.data <- ggplot( (cleanCurated_BivData %>% filter(strain =="KAZ" ) %>%  filter(hand.foci.count == "2") %>%  filter(sex == "male")  ) , aes(y = IFD1_PER, x= fileName, color=chromosomeLength))+geom_point()+ggtitle("Interfocal Distances, ABS KAZ")+facet_wrap(~mouse, scales = "free")+ylim(c(0,1))

nrm.IFD_KAZ.female_BIV.data <- ggplot( (cleanCurated_BivData %>% filter(strain =="KAZ" ) %>%  filter(hand.foci.count == "2") %>%  filter(sex == "female")  ) , aes(y = IFD1_PER, x= fileName, color=chromosomeLength))+geom_point()+ggtitle("Normalized Interfocal Distances, female KAZ")+facet_wrap(~mouse, scales = "free")+ylim(c(0,1))
nrm.IFD_KAZ.female_BIV.data

@@

@@

```{r Q2.totSC_male.first.comp, echo=FALSE}
#move to Q2
Q1.male.Dom.Musc.t.test <- t.test( ( mouse.total.skel %>% filter(sex == "male") %>% filter(subsp == "Dom") )$mean.skel,
(mouse.total.skel %>% filter(sex == "male") %>% filter(subsp == "Musc") )$mean.skel)

@@

@@

The molf male t-tests don't work because I only have total Sc measures for 1 MOLF male.

@@

Q2.all.BIV_t.test_HL <- t.test((cleanCurated_BivData %>%filter(sex == "male")%>%filter(Rec.group == "0") )$chromosomeLength,
              (cleanCurated_BivData %>%filter(sex == "male")%>%filter(Rec.group == "1"))$chromosomeLength)

@@

#DOM-MUSC-ALL
Q2.all.BIV_t.test_DomMusc <- t.test((cleanCurated_BivData %>%filter(subsp == "Dom")%>%filter(sex == "male") )$chromosomeLength,
              (cleanCurated_BivData %>% filter(subsp == "Musc")%>%filter(sex == "male"))$chromosomeLength)
#p-value = 4e-13

#DOM-MOL-ALL
Q2.all.BIV_t.test_DomMol <- t.test((cleanCurated_BivData %>%filter(subsp == "Dom")%>%filter(sex == "male") )$chromosomeLength,
              (cleanCurated_BivData %>% filter(subsp == "Mol")%>%filter(sex == "male"))$chromosomeLength)
#p-value = 6e-10

@@

Q2.SC_BivData_low.rec <- cleanCurated_BivData %>% filter(sex=="male") %>% filter( hand.foci.count < 5)%>% filter(Rec.group == 0 )
Q2.SC_BivData_high.rec <- cleanCurated_BivData %>% filter(sex=="male") %>% filter( hand.foci.count < 5) %>% filter(Rec.group == 1 )

@@

Q2.SC_BivData <- cleanCurated_BivData %>% filter(sex=="male") %>% filter( hand.foci.count < 5)

@@

Q2.glm_mus.av_1COpos_M4 <- glm(mean_1CO.pos.PER ~ subsp * strain, data = (mouse.level.BivData_table  %>% filter(sex == "male") %>% filter(species == "M.musculus") ) )
